---
title: "Interpretable Retail Demand Modeling"
format:
  html:
    toc: true
    number-sections: true
execute:
  echo: true
  warning: false
  message: false
---

## Overview

This notebook turns a course-originated grocery-sales analysis into a portfolio-style project.
The goal is not to re-submit coursework structure, but to evaluate how **model family, heterogeneity controls, and validation design** affect future-week forecasting conclusions.

## Project question

> When predicting overdispersed weekly grocery demand, are the main gains coming from count-model choice, from heterogeneity controls, or from better validation design?

## Setup

```{r}
source("../src/05_run_model_comparison.R")
```

## Load saved outputs

```{r}
model_summary <- readr::read_csv("../results/stage2_model_summary.csv", show_col_types = FALSE)
coef_stability <- readr::read_csv("../results/stage2_coef_stability.csv", show_col_types = FALSE)
nb_checks <- readr::read_csv("../results/stage2_nb_checks.csv", show_col_types = FALSE)
model_summary
```

## Key result

The strongest result is that adding `UPC` and `STORE_NUM` fixed effects materially improves time-aware forecasting performance, while DISPLAY interactions add only marginal extra value.

```{r}
coef_stability
```

## Negative binomial robustness check

```{r}
nb_checks
```

## Interpretation

The portfolio version supports three claims:

1. Overdispersion is real, so count-based modelling is sensible.
2. Product/store heterogeneity matters more than small interaction extensions.
3. Future-week validation changes which modelling choices matter most.

## Caution

This is a **predictive** project, not a causal one.  
Price and promotion coefficients should be read as conditional associations under observed store–product–week variation.
